### 2022-09-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_interpreting_probabilities@19c4344232e59c0b654415ecee53f4854f83c201 🚀

stuff - why we even have probabilistic networks to start with (or
something like that).

\begin{quote}
probably a dope conceptual figure
\end{quote}

\hypertarget{overview-of-probabilities-and-metawebs}{%
\section{Overview of Probabilities and
Metawebs}\label{overview-of-probabilities-and-metawebs}}

How are we defining what the probability of an interaction is (there are
many ways to slice this cake). What does a probability in the context of
a metaweb mean? Can we turn this into a local network realisation that
is also probabilistic and intuitive?

\hypertarget{non-ecological-networks}{%
\section{Non-ecological Networks}\label{non-ecological-networks}}

What can we learn from other systems/fields \emph{e.g.} social networks,
probabilistic graph theory?

@@

A cautionary tale of how we define probabilities?

@@

Regional can inform local but can local inform regional?

@@

what even are probabilities? What is the probability that we will ever
know the answer to that?

>>>>

Why it is useful think about interactions as probabilistic event An
interaction is probabilistic since two species `meeting' does not mean
that an interaction will occur e.g.~a lion crossing paths with a gazelle
does not mean predation will happen but is contextual on the
physiological state of both the lion and the gazelle. Also, two species
co-occurring does not mean there's gonna meet (think of species relative
abundances)

Aim: Although it makes sense to think about interactions as
probabilities it is not without challenges. This paper aims to outline
some of these challenges/limitations of interpreting these probabilities

\begin{quote}
probably a dope conceptual figure {[}`scale' up a the nodes from and
individual to population to taxo group how would how we interpret these
probabilities change{]}
\end{quote}

\hypertarget{overview-of-probabilities}{%
\section{Overview of Probabilities}\label{overview-of-probabilities}}

How are we defining (in the literature) what the probability of
interaction is (there are many ways to slice this cake)? Weighted
Networks??? It might not be as intuitive as you would think/assume

\hypertarget{probabilistic-metawebs}{%
\section{Probabilistic Metawebs}\label{probabilistic-metawebs}}

What does a probability in the context of a metaweb mean? Can we turn
this into a local network realisation that is also probabilistic and
intuitive? Bayesian vs frequentist

@@

A cautionary tale of how we define probabilities? Environmental context,
local abundance context Talk about individual scale and the population
scale (probability at the individual level vs the species level)
Taxonomic scale {[}`scale' up the nodes from an individual to population
to taxo group how would we interpret these probabilities change. How
does the aggregation change the interpretation? Does it?{]} How is it
analogous to spatial and temporal scaling (basically, all kinds of
scaling are just different ways to aggregate individuals/nodes).

@@

Note scaling can refer to both space and time Regional can inform local
but can local inform regional? Network area relationships (Ontario
lakes?? Or Alaska) Why probabilistic realised networks scale with area
but not probabilistic metawebs

@@

\emph{Non-ecological Networks:} What can we learn from other
systems/fields e.g. social networks, probabilistic graph theory?

What even are the probabilities? What is the probability that we will
ever know the answer to that?

Be careful how we define probabilities. Be sure to be explicit about
these things/think about it carefully. Also, different interpretations
imply different scaling, and different ways to manipulate these numbers.
\emph{Maybe mention/thinking about workflow from metaweb to realisation}

Scores vs probabilities
